\documentclass[a4paper,11pt]{article}

\usepackage[a4paper,left=1.2cm,right=1.2cm,top=1.6cm,bottom=1.6cm]{geometry}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{ragged2e}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{lastpage}
\usepackage[T1]{fontenc}
\usepackage{palatino}

\definecolor{linkpink}{RGB}{140,21,21}
\definecolor{lightgray}{gray}{0.7}

\newcommand{\sepspace}{\vspace{6pt}}
\newcommand{\me}{\underline{Weidi Luo}}
\newcommand{\eq}{$^*$}
\newcommand{\link}[2]{\textcolor{linkpink}{\href{#1}{\textbf{#2}}}}
\newcommand{\paper}[6]{\item[#1] #3. \link{#2}{#4}. In \textit{#5}. #6}
\newcommand{\cventry}[5]{\raggedleft \textbf{#1} & #2\\ \raggedleft #3 & #4\\ & #5\\}
\newcommand{\employmententry}[5]{\raggedleft \textbf{#1} & {#2}\\ \raggedleft #3 & #4~~\textcolor{gray}{#5}\\}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[L]{\footnotesize Weidi Luo}
\fancyfoot[R]{\footnotesize Last updated: \today. Page~\thepage~of~\pageref{LastPage}}

\begin{document}

\begin{center}
    \Large{\textbf{\textsc{Weidi Luo}}}
\end{center}

\vspace{-18pt}
\noindent\rule{\textwidth}{0.4pt}
\vspace{0.5em}

\noindent
\begin{minipage}[t]{0.54\textwidth}
    \faEnvelope~\textcolor{linkpink}{\href{mailto:luo.1455@uga.edu}{luo.1455@uga.edu}}\\
    \faHome~\textcolor{linkpink}{\href{https://eddyluo.com/}{eddyluo.com}}\\
    \faGoogle~\textcolor{linkpink}{\href{https://scholar.google.com/citations?user=EZzmjVUAAAAJ}{google scholar}}\\
    \faGithub~\textcolor{linkpink}{\href{https://github.com/EddyLuo1232}{github.com/EddyLuo1232}}\\
    \faTwitter~\textcolor{linkpink}{\href{https://x.com/luoweidi84}{x.com/luoweidi84}}\\
    \faLinkedin~\textcolor{linkpink}{\href{https://www.linkedin.com/in/weidi-luo-aa02b5242}{linkedin.com/in/weidi-luo}}
\end{minipage}
\begin{minipage}[t]{0.46\textwidth}
    \raggedleft
    School of Computing\\
    University of Georgia\\
    Athens, GA\\
    United States\\
\end{minipage}

\sepspace
\section*{Research Overview}

My research focuses on \textbf{AI safety and security}, with a particular emphasis on trustworthy foundation models, including multimodal and reasoning models, and autonomous AI agents. Across my research and industry experience, I study how advanced models fail under realistic adversarial, privacy, and security threats, and how to build evaluations and safeguards that remain effective in deployment.

\begin{itemize}[leftmargin=1.2em,itemsep=2pt,topsep=4pt]
    \item[$\circ$] \textbf{AI Safety and Security}: detecting real-world threats, jailbreak and privacy-risk analysis, mechanistic safety analysis, and risk mitigation for foundation models.
    \item[$\circ$] \textbf{Agent Safety}: adaptive agent guardrails, agent interpretability, computer-use and coding-agent red-teaming, and real-world threat benchmarking.
    \item[$\circ$] \textbf{AI for Security Applications}: vulnerability discovery, cybersecurity evaluation, and security-focused applications of foundation models and AI agents.
\end{itemize}

\sepspace
\section*{Education}

\begin{tabular}{p{4.1cm}@{\hspace{1em}}!{\textcolor{lightgray}{\vrule width 0.5pt}}@{\hspace{1em}}l}
    \raggedleft \textbf{Ph.D. Student} & University of Georgia, School of Computing\\
    \raggedleft CS & Advisor: Zhen Xiang\\
    \raggedleft Aug 2025 -- Present & Co-advised by Chaowei Xiao, Johns Hopkins University\\
    & \\

    \raggedleft \textbf{B.A.} & The Ohio State University, College of Arts and Sciences\\
    \raggedleft CS & Advisors: Chaowei Xiao, Yu Li, Ruixiang Tang, and Yu Su\\
    \raggedleft Aug 2022 -- Jul 2025 & \\
\end{tabular}

\sepspace
\section*{Industry Experience}

\begin{tabular}{p{4.1cm}@{\hspace{1em}}!{\textcolor{lightgray}{\vrule width 0.5pt}}@{\hspace{1em}}l}
    \employmententry{Research Intern}{Meta Superintelligence Labs}{Jun 2026 -- Present}{Menlo Park, CA, USA}{Advisor: Bo Li}
    & \\

    \employmententry{Research Intern}{Virtue AI}{May 2026 -- Jun 2026}{San Francisco, CA, USA}{Advisor: Zhaorun Chen}
    & \\

    \employmententry{MLE Intern}{IDEA}{Jul 2024 -- Oct 2024}{Shenzhen, Guangdong, China}{Advisor: Yu Li}
\end{tabular}

\sepspace
\section*{Research Experience}

\begin{tabular}{p{4.1cm}@{\hspace{1em}}!{\textcolor{lightgray}{\vrule width 0.5pt}}@{\hspace{1em}}l}
    \cventry{Research Intern}{Johns Hopkins University}{Dec 2023 -- Apr 2025}{Department of Electrical and Computer Engineering}{Advisor: Chaowei Xiao}
    & \\

    \cventry{Research Intern}{Rutgers University}{Oct 2024 -- Dec 2024}{Department of Computer Science}{Advisor: Ruixiang Tang}
    & \\

    \cventry{Research Assistant}{ICICLE Institute, The Ohio State University}{Apr 2023 -- Aug 2023}{College of Engineering}{Advisor: Yu Su}
\end{tabular}

\sepspace
\section*{Honors and Awards}

\begin{tabular}{p{14cm}@{\hspace{1em}}!{\textcolor{lightgray}{\vrule width 0.5pt}}@{\hspace{1em}}l}
    SoC Graduate Student Research Award, University of Georgia & 2026\\
    \$20,000 SafeBench Prize, Center for AI Safety & 2025\\
\end{tabular}

\sepspace
\section*{Selected Publications}
The~\eq~sign denotes equal contribution.

\subsection*{Peer-Reviewed Papers}
\begin{enumerate}[leftmargin=2.4em,itemsep=4pt]

\paper
    {C6}
    {https://arxiv.org/pdf/2504.19373}
    {\me\eq, Tianyu Lu\eq, Qiming Zhang\eq, Xiaogeng Liu, Bin Hu, Yue Zhao, Jieyu Zhao, Song Gao, Patrick McDaniel, Zhen Xiang, and Chaowei Xiao}
    {Doxing via the Lens: Revealing Location-related Privacy Leakage on Multi-modal Large Reasoning Models}
    {International Conference on Learning Representations (ICLR)}
    {2026.}

\paper
    {C5}
    {https://arxiv.org/abs/2502.11448}
    {\me, Shenghong Dai, Xiaogeng Liu, Suman Banerjee, Huan Sun, Muhao Chen, and Chaowei Xiao}
    {AGrail: A Lifelong Agent Guardrail with Effective and Adaptive Safety Detection}
    {Annual Meeting of the Association for Computational Linguistics (ACL) Main}
    {2025.}

\paper
    {C4}
    {https://arxiv.org/abs/2404.03027}
    {\me\eq, Siyuan Ma\eq, Xiaogeng Liu\eq, Xiaoyu Guo, and Chaowei Xiao}
    {JailBreakV-28K: A Benchmark for Assessing the Robustness of MultiModal Large Language Models against Jailbreak Attacks}
    {Conference on Language Modeling (COLM)}
    {2024. \textcolor{gray}{Winner of the \$20,000 SafeBench Prize; integrated into NVIDIA/garak and Microsoft's PyRIT.}}

\paper
    {C3}
    {https://arxiv.org/abs/2410.17922}
    {\me\eq, He Cao\eq, Yu Wang, Zijing Liu, Aidan Wong, Bin Feng, Yuan Yao, and Yu Li}
    {Dynamic Guided and Domain Applicable Safeguards for Enhanced Security in Large Language Models}
    {Annual Conference of the North American Chapter of the Association for Computational Linguistics (NAACL) Findings}
    {2025.}

\paper
    {C2}
    {https://arxiv.org/abs/2411.13504}
    {Mingyu Jin, \me, Sitao Cheng, Xinyi Wang, Wenyue Hua, Ruixiang Tang, William Yang Wang, and Yongfeng Zhang}
    {Disentangling Memory and Reasoning Ability in Large Language Models}
    {Annual Meeting of the Association for Computational Linguistics (ACL) Main}
    {2025.}

\item[C1] Vardaan Pahuja, \me, Yu Gu, Cheng-Hao Tu, Hong-You Chen, Tanya Berger-Wolf, Charles Stewart, Song Gao, Wei-Lun Chao, and Yu Su. \textcolor{linkpink}{\textbf{Bringing Back the Context: Image Classification as Link Prediction on Multimodal Knowledge Graphs}}. In \textit{ACM International Conference on Information and Knowledge Management (CIKM) Oral}. 2024.

\end{enumerate}

\subsection*{Workshop Papers}
\begin{enumerate}[leftmargin=2.4em,itemsep=4pt]

\paper
    {W2}
    {https://arxiv.org/abs/2510.06607}
    {\me, Qiming Zhang, Tianyu Lu, Xiaogeng Liu, Bin Hu, Hung-Chun Chiu, Siyuan Ma, Yizhe Zhang, Xusheng Xiao, Yinzhi Cao, Zhen Xiang, and Chaowei Xiao}
    {Code Agent can be an End-to-end System Hacker: Benchmarking Real-world Threats of Computer-use Agent}
    {ICML AIWILD Workshop (Oral)}
    {2026.}

\end{enumerate}

\subsection*{Preprints}
\begin{enumerate}[leftmargin=2.4em,itemsep=4pt]

\paper
    {P3}
    {https://arxiv.org/pdf/2606.22673}
    {\me, Qiming Zhang, Yihao Quan, Mingyu Jin, Jie Cai, Chaowei Xiao, Jingcheng Niu, and Zhen Xiang}
    {AgentLens: Interpretable Safety Steering via Mechanistic Subspaces for Multi-Turn Coding Agent}
    {arXiv Preprint}
    {2026.}

\paper
    {P2}
    {https://arxiv.org/pdf/2604.01444}
    {\me\eq, Xiaofei Wen\eq, Tenghao Huang\eq, Hongyi Wang, Zhen Xiang, Chaowei Xiao, Kristina Gligoric, and Muhao Chen}
    {Cooking Up Risks: Benchmarking and Reducing Food Safety Risks in Large Language Models}
    {arXiv Preprint}
    {2026.}

\paper
    {P1}
    {https://arxiv.org/abs/2405.20773}
    {Siyuan Ma\eq, \me\eq, Yu Wang, Xiaogeng Liu, Muhao Chen, Bo Li, and Chaowei Xiao}
    {Visual-RolePlay: Universal Jailbreak Attack on MultiModal Large Language Models via Role-playing Image Character}
    {arXiv Preprint}
    {2024.}

\end{enumerate}

\sepspace
\section*{Professional Service}

\subsection*{Conference Reviewing}
\begin{tabular}{p{14cm}@{\hspace{1em}}!{\textcolor{lightgray}{\vrule width 0.5pt}}@{\hspace{1em}}l}
    Annual Meeting of the Association for Computational Linguistics (ACL) & 2025, 2026\\
    Empirical Methods in Natural Language Processing (EMNLP) & 2025\\
    European Chapter of the Association for Computational Linguistics (EACL) & 2026\\
    International Conference on Machine Learning (ICML) & 2026\\
    Conference on Language Modeling (COLM) & 2026\\
    Neural Information Processing Systems (NeurIPS) & 2026\\
\end{tabular}

\sepspace
\section*{Hobbies}

\begin{tabular}{p{14cm}@{\hspace{1em}}!{\textcolor{lightgray}{\vrule width 0.5pt}}@{\hspace{1em}}l}
    Violin, Level 10, Sichuan Musicians Association & \\
\end{tabular}

\end{document}
